---
title: "simplexgb workflow"
author: "Prasanna Bhogale"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Data munging is hard, needs intuition and craftsmanship, but most ML issues are quite standard once the data has been understood. `simplexgb` is intended to help you handle most ML usecases without straying too far from the [tidyverse](https://www.tidyverse.org/), while still utilizing the versatility and scalability of [xgboost](https://xgboost.readthedocs.io/en/latest/). To setup xgboost correctly on your system so that it uses all your cores/GPUs to train, see [this page](https://xgboost.readthedocs.io/en/latest/build.html).

## The workflow

Before attempting any machine learning, you should do your best to understand your data and develop some intuition for what it is telling you. If you are new to data science, there is no better place to start than [R for data science](https://r4ds.had.co.nz/).
To framed the business/scientific challenge you are tackling in terms of a classification or regression problem, you should have have a *target variable* and other variables that provide some information pertinent to predicting the value of the target variable, these are called *predictors*. 

1. **Tidy data :** this term refers to an organization of your data so that each row is one observation (one instance of known values of predictors and the known value of the target variable), and is explained [here](http://vita.had.co.nz/papers/tidy-data.html).

We first illustrate the workflow with a regression problem, and then repeat the steps with a classification problem. We are going to use weather data from NASA. 

2. **Preparing the training data :** xgboost requires the data to be in a particular format, for example, categorical variables need to be encoded as factors and then converted to a simple binary format via a process called [one hot encoding](https://en.wikipedia.org/wiki/One-hot). The `prepare_training_set` function takes in your data frame and the name of your target variable and does all the leg work for you, putting together a data structure that other functions from `simplexgb` can work with. 

```{r}
library(mlbench)
library(tidyverse)
data(BreastCancer)
df <- BreastCancer %>% 
  select(-Id)
df %>% head()
train_struct <- prepare_training_set(df = df, target_variable = 'Class')
```

3. **Guess hyperparameters :** `simplexgb` takes some reasonable values of relevant hyperparameters depending on the size of your data set. You can tune these for better performance as you iterate. For now, we will simply take the default guesses that `simplexgb` generates for us. 

```{r}
hyp <- guess_hyperparameters(train_structure = train_struct)
hyp %>% print()
```

`simplexgb` has spotted our problem to be a classification problem and chosen an appropriate objective function and evaluation metric. 

4. **Evaluate performance :** For any dataset (that includes some work on feature engineering) and a set of hyperparameters, we should evaluate how well a model with those hyperparameters trained on that dataset will perform using cross validation. 

```{r}
cv_results <- cross_validate(train_structure = train_struct, hyperparameters = hyp, nfold = 5)
print(cv_results$metric)
hyp_more <- guess_hyperparameters(train_structure = train_struct, n_estimators = 50000)
cv_results_more <- cross_validate(train_structure = train_struct, hyperparameters = hyp_more, nfold = 5)
print(cv_results_more$metric)
```
Just to illustrate the point, we added more estimators and obrained a marginal improvement in our metric. the `cv_results` structure has a lot of information useful for evaluating a model, but it is summarised in one number, the metric averaged over the folds of the CV. 

5. **Train the model :** We keep aside a few observations to test our model with, and use the rest of our data to train a model.

```{r}
smp_size <- floor(0.75 * nrow(df))
set.seed(123)
train_ind <- sample(seq_len(nrow(df)), size = smp_size)

train_df <- df[train_ind, ]
test_df <- df[-train_ind, ]

train_struct <- prepare_training_set(train_df, target_variable = 'Class')
hyp <- guess_hyperparameters(train_structure = train_struct, n_estimators = 1000000, depth = 7)
xgbmodel <- train_model(train_structure = train_struct, hyperparameters = hyp)
```


6. **Predict on the test set :** Nothing could be simpler. 

```{r}
pred_df <- get_predictions(xgbmodel, test_df = test_df)
pred_df %>% head()
test_df_preds <- test_df %>% 
  mutate(preds = pred_df$category)
table(test_df_preds$Class, test_df_preds$preds)
```

